From physical principles to ???

### 2016-04-15 2015CompleteDerivation/completeDerivation.tex
Starting to tackle classical phase space

Also: we can search for omega looking from constraints. Must be linear. Must be skew-symmetric (applied to the same vector twice must be zero). Must be invariant by coord transformation.

>>>>

The ability to associate finite amount of material with sets of states allows us to define finite regions of $\mathcal{S}$ and compare them. Consider a region of position and momentum in phase space. If we are able to spread a finite amount of material into a uniform distribution, then we know we have a finite region. And the density will give us an indication of how big the region is: if we double the region, the density will half. In other words: because we are describing densities over $\mathcal{S}$, we are able to give a unique way to measure the size of sets of $\mathcal{S}$, a metric $d\mu$ and our positive linear functionals become integrals: $\Lambda_U (\mathcal{c}) : \int_U \rho_{\mathcal{c}} d \mu$.
